The flux emitted by an SNIa in the UV, optical and NIR traces the comptonization of the photons emitted through the $^{56}$Ni $\rightarrow$  $^{56}$Co $\rightarrow$ $^{56}$Fe decay chain \citep[see][]{Nadyozhin1994}.
As the SN emits most of its flux in the UV to NIR passbands, the "uvoir bolometric flux" represents a physically meaningful quantity \citep{Suntzeff1996}

We select a low-reddening sample with objects that have a host extinction less than $0.1 mag$. This makes our measurements are less sensitive to a reddening law. 
For objects with sufficient amount of near maximum data in the optical and the NIR, we construct UBVRIJH bolometric light curves. We do not use $K$ band data since there are very few objects in the sample with well-sampled $K$ band light curves. Using  objects that have well-sampled $K$ light curves we calculate the flux emitted in the $K$ band and find that it is between $1-3 \%$. Thus, not using the $K$-band is not a dominant source of uncertainty. 
The magnitudes were corrected 
for reddening using a CCM reddening law for each filter. The values for the extinction are presented in table \ref{tab:mni}. The uncertainty in the reddening estimate
was propagated into the calculation of the bolometric flux
Using zero-points in the given filters, the magnitudes were converted to fluxes. The data in the different filters is interpolated, instead of using a reference filter. The filters are integrated using the trapezoidal rule.
The resulting light curve, in ergs/$cm^2$/s  was converted into an absolute bolometric light curve 
by using the distances of the SN derived from the host galaxy redshift. 

Since all distances are scaled to an $H_0=70 km s^{-1} Mpc ^{-1}$the errors in the luminosity distance are only affected by the relative errors in the 
distance moduli (see Table \ref{tab:mni} for values and uncertainty estimates). For objects not in the hubble flow, we use distance measurements from published estimates (which use others methods eg. Cepheid, Tully-Fisher relation etc.). 

In our sample, for uniformity, we restrict the analysis to objects with coverage from $u-H$ bands with coverage around the bolometric peak.

\input{tab/sn_samp_lr.tex}





